\documentclass[UKenglish]{latex/atlasdoc}
\usepackage{latex/atlaspackage}
\usepackage{latex/atlasphysics}
\usepackage{latex/atlascontribute}

\usepackage{xspace}
\usepackage{multirow}
%\usepackage{verbatim}


\graphicspath{{logos/}{figures/}}


% Title, abstract and document 
\input{atlas-document-metadata}
\input{ambslp-defs}

\begin{document}
	
\maketitle

\tableofcontents

\section{Introduction}
This document describes  the structure, working principle and use cases for
the online software package used to
control the associative memory board, then referred as AMB or AMBSLP.
The software is contained in the package
\hyperlink{https://svnweb.cern.ch/trac/atlastdaq/browser/FTK/ambslp?order=name}
	{FTK/ambslp}
and managed by the AMB team. Instruction on how to compile the
package within the ATLAS TDAQ software framework are provided elsewhere,
with all required details. Indeed, the following documentation assumes knowledge
on how to compile it and provide information for both users and developers,
in order to provide documentation on how to control the board and
add or maintain the main functionalities.

More specifically,
the software  package provides:
\begin{itemize}
  \item a library containing low level functions
  used to control the board;

	\item a module loaded by the ATLAS run control (RC) to control the board,
	associated with the board description within this framework, base monitoring
    tools and more;
    
	\item a set of standalone tools, as compiled programs and scripts,
	used to control and monitor the board from a command line shell.
\end{itemize} 

The document goals are to both support the experts to verify
the behavior of a board, fixing eventual issues, as well as the developer to
change to evolve the code. The document will also try to document
the RC related parts and standalone software.

An initial section will be devoted to document some basic features of the boards,
related to its working principle, related to firmware and electronic characteristics.
The following section will provide more detailed information on the software components
designed to allow a correct working of the board and allowing to control
in different scenarios.

\section{Associative board working principle and features}
\input{ambslp_boarddesc}

\section{Configure and control the board standalone tools}

\subsection{Control the board status}
To control the board status the main available command is
\textbf{\texttt{ambslp\_status\_main}}. This should be
launched from the VME SBC or in a node where the ATLAS Information
Service (IS) available.

The command line options are limited. The most important are the \textbf{slot} 
number, used to set the VME slot where the board in installed and
the partition name, used to eventually retrieve the board
information from IS.

In both cases the output is printed on the screen and can be quite 
verbose, for this reason an example will be presented here in
pieces.

\begin{itemize}
	\item The first part reports if the data are from IS or not and the
	firmware version uploaded into the FPGAs:
	\begin{verbatim}
	++++++++++++++++++++++++++
	ambslp_status(), read from IS:
	0Hit Firmware version:  0xd220a7df
	CONTROL Firmware version:  0x4
	VME Firmware version:  0x521
	ROAD Firmware version:  0x2a210413
	\end{verbatim}
	in case of problem  the firmware version  can be 0xffffffff or 0x0, 
	both values are commonly related to a configuration issue.
	
	\item The following part reports the temperature on the LAMBs:
\begin{verbatim}
++++++++++++++++++++++++++
Temperature measurements
VME slot front | LAMB2 | LAMB2 | LAMB0 | LAMB0 | VME back plane
VME slot front | LAMB3 | LAMB3 | LAMB1 | LAMB1 | VME back plane
|    0  |    0  |   34  |   32  |
|   28  |   29  |   29  |   28  |
\end{verbatim}		
	the reported values are organized in rows and columns, reporting
	the geographical organization of the LAMBs within the AMB. A $0$
	temperature usually means that no card is installed in a specific slot,
	$255$ means that the sensore is not instlled or not working,
	better information can be assessed checking for the board information
	into EDMS.

	\item The following bloc reports the status of the HIT FPGA. At the
	begin of this long output section the eventual test-mode (TMODE) and
	PLL locks are reported, the presence mask of the LAMBs, then hold and 
	empty status for the input FIFOs.
	for the links
\begin{verbatim}
++++++++++++++++++++++++++
HIT STATUS
TMODE:           1
PLL lock:        f
PLL REF LOCK:    0

LAMB mask:  f00

SCT hold status:  0
PIX hold status:  a6

SCT empty status:  6
PIX empty status:  0
\end{verbatim}
	The presence mask is a 4-digit number where \textbf{0} means the 
	\emph{card is present}, \textbf{f} the \emph{card is missing}, the
	example can be read as f00=0f00, that means LAMB 2 is missing.

	\item The next portion of the HIT report section represents the
	alignment of the serial links to the chips and the AUX.
\begin{verbatim}
GTP align QUAD216:  1 - 1 - 1
GTP align QUAD213:  1 - 1 - 1
GTP align QUAD116:  1 - 1 - 1
GTP align QUAD113:  1 - 1 - 1

GTP reset done QUAD 216 RX:  f - TX f
GTP reset done QUAD 213 RX:  f - TX f
GTP reset done QUAD 116 RX:  f - TX f
GTP reset done QUAD 113 RX:  f - TX f
\end{verbatim}

	\item The final part of the HIT summary shows the HIT FSM satus,
	useful in case of debugging of the board, the input rates and the number
	of errors in each link.
\begin{verbatim}
HIT SCT FSM status: 0x1121
HIT PIX FSM status: 0x1111

ch 0    ch 1    ch 2    ch 3    ch 4    ch 5    ch 6    ch 7   ch 8     ch 9    ch 10   ch 11
HOLD  1s        5e-08   4e-08   4e-08   4e-08   1.51812 0.00133648      1.5059 0.00656278       1.51965 0.00053916      1.50891 0.0108022
EMPTY 1s        1.51084 1.51084 1.51085 1.51086 2.38e-06        1.09e-06       2.49e-06 1.05e-06        2.25e-06        1.16e-06        2.31e-06        1.04e-06

Lost of Sync error counter. For each link count 0-255 and then wrap around.
SCT link 0:    00
SCT link 1:    00
SCT link 2:    00
SCT link 3:    00
PIX link 0_0:  00
PIX link 0_1:  00
PIX link 1_0:  00
PIX link 1_1:  00
PIX link 2_0:  00
PIX link 2_1:  00
PIX link 3_0:  00
PIX link 3_1:  00
\end{verbatim}

	\item The next part of the staus represents the CTRL FPGA, where
	the FSM state in controlling HIT and ROAD FPGAs are reported. The
	block is self-explanatory
\begin{verbatim}
++++++++++++++++++++++++++
CONTROL STATUS
Firmware:        15 v.4
FSM state Hit:   1
FSM state Road:  2

Control FSMs are documented in Figure 4, section 1.2.1 of the AM board documentation.
FSM state HIT:  0 = wait for initial global init
1 = send hits event N; wait for HIT end event on all channels and for DONE ROAD previous event
2 = wait X cycles
3 = DONE HIT event N, send INIT_EV
4 = wait a few cycles
FSM state ROAD: 0 = wait for initial global init
2 = DONE ROAD event N-1
1 = send ROAD to AUX event N-1
3 = wait a few cycles
\end{verbatim}

	\item The following block of messages refers to the ROAD FPGA. 
\begin{verbatim}
++++++++++++++++++++++++++
ROAD STATUS
Firmware:      14 v.1
TMODE:         0
PLL lock:      f
PLL REF LOCK:  0

Hold Aux status:  0

Empty Fifo Lamb_0 Status:      f
Empty Fifo Lamb_1 Status:      f
Empty Fifo Lamb_2 Status:      f
Empty Fifo Lamb_3 Status:      f

Prog Full Fifo Lamb_0 Status:  0
Prog Full Fifo Lamb_1 Status:  0
Prog Full Fifo Lamb_2 Status:  0
Prog Full Fifo Lamb_3 Status:  0

ROAD input link UP QUAD216:  c
ROAD input link UP QUAD213:  f
ROAD input link UP QUAD116:  c
ROAD input link UP QUAD113:  f

GTP reset done QUAD 216 RX:  f - TX f
GTP reset done QUAD 213 RX:  f - TX f
GTP reset done QUAD 116 RX:  f - TX f
GTP reset done QUAD 113 RX:  f - TX f
\end{verbatim}
	The first registers
	report on the test-mode flag and the PLL locks. The eventual hold signals from the 
	AUX are also reported. The are then the registers related to the empty or full 
	status for the FIFOs that collect the output from each LAMB, 
	
	\item 
\begin{verbatim}
LAMB = 0
Missing patternX link 0 = 0x0 0x0 0x0 0x0
Missing patternX link 1 = 0x0 0x0 0x0 0x0
Missing patternX link 2 = 0x0 0x0 0x0 0x0
Missing patternX link 3 = 0x0 0x0 0x0 0x0
LAMB = 1
Missing patternX link 4 = 0x0 0x0 0x0 0x0
Missing patternX link 5 = 0x0 0x0 0x0 0x0
Missing patternX link 6 = 0x0 0x0 0x0 0x0
Missing patternX link 7 = 0x0 0x0 0x0 0x0
LAMB = 2
Missing patternX link 8 = 0x0 0x0 0x0 0x0
Missing patternX link 9 = 0x0 0x0 0x0 0x0
Missing patternX link a = 0x0 0x0 0x0 0x0
Missing patternX link b = 0x0 0x0 0x0 0x0
LAMB = 3
Missing patternX link c = 0x0 0x0 0x0 0x0
Missing patternX link d = 0x0 0x0 0x0 0x0
Missing patternX link e = 0x0 0x0 0x0 0x0
Missing patternX link f = 0x0 0x0 0x0 0x0
\end{verbatim}

	\item the final part of the \texttt{ambslp\_status\_main} output
	reports the disparity error: from the link:
\begin{verbatim}
LAMB0 RX 8b/10b or disparity errors = 0x0
LAMB1 RX 8b/10b or disparity errors = 0x0
LAMB2 RX 8b/10b or disparity errors = 0xffffffff
LAMB3 RX 8b/10b or disparity errors = 0x0
\end{verbatim}
	there is a 32-bit register available for each LAMB, the number is at
	the begin of the line, and the bits in the word represents the serial
	lines at had at least one disparity error. This bit can only be reset
	with a reinitialization of the board of levels 0 and 2,
	 see \ref{sec:ambslpinit} for more information.
\end{itemize}

\subsection{Initialize the board}
\label{sec:ambslpinit}

The AMB initialization is performed sending a specific command
to the board through the VME bus, this can be done using the 
\textbf{\texttt{ambslp\_init\_main}} program. The program has two
main options: the board slot (\verb|--slot--|)and reset level (\verb|--amb_lamb| 
or positional argument).
Examples of the command line are:
\begin{verbatim}
$ ambslp_init_main --slot 2 --amb_lamb <N>
$ ambslp_init_main --slot 2 <N>
\end{verbatim}

At the moment there are 4 initialization levels available:
\begin{description}
	\item[0] this performs a basic reset of the FSMs, eventual loops
	are stopped, FIFO content and configuration registers are unchanged.
	
	\item[1] this performs a reset of LAMB's FIFOs.
	
	\item[2] performs a cleanup of the AMB's FIFOs.
	
	\item[3] perfoms a full reinitialization of the configuration registers
	in the board.
\end{description}


\subsection{Configure the AM chips}



\subsection{Pattern bank setup}
\label{sec:bankload}

A pattern bank can be loaded from \ldots

\section{High-level procedures}
\label{sec:highlevel}

\input{ambslp_procedures}

\section{Run control module}

\input{ambslp_RC}

\section{AMBoard class and library structure}
\label{sec:library}

The \texttt{ambslp} package is mostly written in C++, requiring C++11 
compatible compilers. It defines the \textbf{\AMBoard} class and other low
level function able to communicate, to spy or change the state of the board.
Most of the 


\appendix
\section{Common example}
\subsection{Configure the board with a random bank}

\begin{verbatim}
$ ambslp_procedure --slot 15 --bankpath random configure load connect
\end{verbatim}

\end{document}